### 2015-04-15 stat343/hw5.tex
Unscrewed up this repo - files I want are followed, everything else removed from rep

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
STAT 343, Homework 5 \hfill Aaron Maurer
\vspace{2mm}
\hrule
\vspace{2mm}
    \item[1.]
                The constant variance assumption apiears to hold; we do not seem to have the variance change over the range of predicted values. The plot on the left, which is the residuals versus the fitted values, indicates by the eyeball test that the distribution of residuals is constant across the range of predicted values. This is shown more formally by the plot on the right, where I have fit a linear model to the square root of the absolute value of each residual in terms of the fitted value. This yields a coefficient of $-.00016$ for the fitted values, with a monstrous p-value of $.969$, dictating that the fitted values of the original regression really don't have any correlation with the deviation of the residuals. \\
                \includegraphics[width=9cm]{hw5_1_a_res} 
                \includegraphics[width=9cm]{hw5_1_a_sqrtres} 
                The normality assumption also seems to hold; it appears the residuals are normally distributed around the predicted values. This is indicated by the eyeball test, where we can see from the quantile-quantile plot that the quantiles of the residuals match the quantiles of a normal distribution fairly closely. Additionally, testing that they are normal formally, the Shapiro-Wilkes test yields a p-value of $.430$, which is far to high to reject normality.
                    \includegraphics[width=9cm]{hw5_1_b_qq} 
                We do see some points with large leverage, but it doesn't seem that any stand out as being unusually large. I have made a quantile-quantile plot of the leverages against the half normal distribution. We see the states with the highest leverage are Utah followed by California. However, they don't appear to be particular extreme or out of line with the other leverages.
                    \includegraphics[width=9cm]{hw5_1_c_halfnorm} 

@@

                So in the expectation, you would get the same $\beta$ irrespective of the variance level.

@@

@@

                This is essentially two separate models. Since the original model corresponds to a subspace of this model (where the coefficient on the first variable is $0$ and the second two hav equal coefficients), we can compare the two models with a $F$ test: \\

@@

        \[HA+eB=I, \, HB+eC=0, \, e^TA+fB^T=0, \, e^TB+fC=I\]

@@

        Plugging everything in and multiplying $MM^{-1}$, I get the desired result, so my initial assumption appears to be correct.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
STAT 343, Homework 5 \hfill Aaron Maurer
\vspace{2mm}
\hrule
\vspace{2mm}
\begin{itemize}
    \item[1.]
        \begin{itemize}
            \item[a)] 
                The constant variance assumption appears to hold; we do not seem to have the variance change over the range of predicted values. The plot on the left, which is the residuals versus the fitted values, indicates by the eyeball test that the distribution of residuals is constant across the range of predicted values. This is shown more formally by the plot on the right, where I have fit a linear model to the square root of the absolute value of each residual in terms of the fitted value. This yields a coefficient of $-.00016$ for the fitted values, with a monstrous p-value of $.969$, dictating that the fitted values of the original regression really don't have any correlation with the deviation of the residuals. \\
                \includegraphics[width=9cm]{hw5_1_a_res} 
                \includegraphics[width=9cm]{hw5_1_a_sqrtres} 
            \item[b)]
                The normality assumption also seems to hold; it appears the residuals are normally distributed around the predicted values. This is indicated by the eyeball test, where we can see from the quantile-quantile plot that the quantiles of the residuals match the quantiles of a normal distribution fairly closely. Additionally, testing that they are normal formally, the Shapiro-Wilkes test yields a p-value of $.430$, which is far to high to reject normality.
                \begin{center}
                    \includegraphics[width=9cm]{hw5_1_b_qq} 
                \end{center}
            \item[c)]
                We do see some points with large leverage, but it doesn't seem that any stand out as being unusually large. I have made a quantile-quantile plot of the leverages against the half normal distribution. We see the states with the highest leverage are Utah followed by California. However, they don't appear to be particular extreme or out of line with the other leverages.
                \begin{center}
                    \includegraphics[width=9cm]{hw5_1_c_halfnorm} 
                \end{center}

@@

                So in the expectation, you would get the same $\beta$ irrespective of the variance level. \\

@@

                My conclusion is that we really have two distinct sets of data that can't be modeled with one linear regression.

@@

                This is essentially creating a separate model for each half of the data. Since the original model corresponds to a subspace of this model (where the coefficient on the first variable is $0$ and the second two hav equal coefficients), we can compare the two models with a $F$ test: \\

@@

        \[HA+eB^T=I, \, HB+eC=0, \, e^TA+fB^T=0, \, e^TB+fC=I\]

@@
